A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-12 manuscript.Rmd
set seed for small examples in manuscript
fix typo
correct spelling of Machiavellism

Machiavellianism is higher in male persons.

@@

If you are unfamiliar with the specifics of SEM, we you may skip the next sections and continue in section ["Randome Number Generation"](#prng).
To simulate data in SEM, one first specifies a model (typically in the form of a structural model and a measurement model), selects plausible population values for all parameters, computes the model-implied mean vector and covariance matrix, and then samples as many observations as needed from a multivariate normal distribution following with the given mean vector and covariance matrix.

@@

@@

One way to ensure that you can expect your analysis to work with real data is to simulate data.
We, for example, simulated data for the Machiavellism subscale of the short dark triad (SD3) and analyzed this with structural equation modelling (SEM).
The simulation showed that we have to gather at least `r minn$n_obs` observations per group to archive enough precision and that our solution to a data problem we expect (insufficient measurement invariance) introduces a bias of `r round((est_diff - true_diff)*100/true_diff, 2)`%.
These results are also visualized in Figure \@ref(fig:simulation-plot).
If you went to the trouble to simulate data, we argue that you get a preregistration almost for free.
A preregistration in code describes sufficiently how you want to analyze the data, but ideally, you also convey the why.
Dynamic document generation combines code and text, enabling you to explain your reasoning.
See the section on [R Markdown] for an example of a dynamic document generation paradigm.
In fact, this manuscript and therefore the here presented Machiavialismus example were preregistered as a full manuscript, and you can see the results on real data in section [Reproduce a Project].

>>>>

Machiavellism is higher in male persons.

@@

If you are unfamiliar with the specifics of SEM, you may briefly skim the next sections and continue in section ["Randome Number Generation"](#prng).
To simulate data in SEM, one first specifies a model (typically in the form of a structural model and a measurement model), selects plausible population values for all parameters, computes the model-implied mean vector and covariance matrix, and then samples as many observations as needed from a multivariate normal distribution following with the given mean vector and covariance matrix.

@@

```{r, include=FALSE}
set.seed(1234)
```

@@

One way to ensure that you can expect your analysis to work with real data is to simulate data.
We, for example, simulated data for the Machiavellism subscale of the short dark triad (SD3) and analyzed this with structural equation modelling (SEM).
The simulation showed that we have to gather at least `r minn$n_obs` observations per group to archive enough precision and that our solution to a data problem we expect (insufficient measurement invariance) introduces a bias of `r round((est_diff - true_diff)*100/true_diff, 2)`%.
These results are also visualized in Figure \@ref(fig:simulation-plot).
If you went to the trouble to simulate data, we argue that you get a preregistration almost for free.
A preregistration in code describes sufficiently how you want to analyze the data, but ideally, you also convey the why.
Dynamic document generation combines code and text, enabling you to explain your reasoning.
See the section on [R Markdown] for an example of a dynamic document generation paradigm.
In fact, this manuscript and therefore the here presented Machiavellism example were preregistered as a full manuscript, and you can see the results on real data in section [Reproduce a Project].
